Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-01-03 ongoing/report/article.tex
Use underscore for matrices & vectors; Ready to reduce length of survey

\author{Tzu-Yu Jeng}
\date{\today}
\title{Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound}

\newcommand{\MB}[1]{\mathbb{#1}}
\newcommand{\MC}[1]{\mathcal{#1}}
\newcommand{\MF}[1]{\mathfrak{#1}}
\newcommand{\RM}[1]{\mathrm{#1}}
\newcommand{\T}[1]{\tilde{#1}}
\newcommand{\V}[1]{\stackunder[1.2pt]{$#1$}{\rule{.9ex}{.075ex}}}
\newcommand{\M}[1]{\V{\V{#1}}}

\newcommand{\LA}{\langle}
\newcommand{\RA}{\rangle}

@@

We restrict our discussion to the Hilbert space over the field of \(\MB{R}\) or \(\MB{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
We use \(\MB{K}\) to refer to either \(\MB{R}\) or \(\MB{C}\).
Lower case Latin alphabets with single underline, like \(\V{a}\), denote vectors, and upper case Latin alphabets with double underlines, like \(\M{A}\), denote matrices.
To avoid being too pedantic, we simply write \(\V{a} \in \MB{C}^N\) to stress \(\V{a}\) is a \(N\)-dimensional vector, and the role it plays in the vector space is understood.
Similarly, we also write \(\V{A} \in \MB{M}(M,N)\) to stress \(\V{A}\) is a \(M\) by \(N\) matrix, and the role it plays as linear transformation is understood.
Inner product is denoted as \(\LA \MB{a}, \MB{b} \RA\).
Slightly abusing notation, denote as \(\V{a}(n)\) the \(n\)-th component of \(\V{a}\), and denote as \(\V{A}(m,n)\) the \((m,n)\)-entry of \(\V{A}\)
Especially, \(\V{u}_n\) is the \(n\)-th unit vector in the Cartesian coordinates (not to be confused with the noise).

@@

\Result
{Definition}
{
\(x \in \MB{K}^N\) is called \(s\)-sparse, if
\begin{gather} 
\# \{\RM{supp}(x)\} \leq s
\end{gather}
That is, only at most \(s\) components of vector \(x\) is nonzero.
}

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
\begin{gather}
\RM{min}_{x' \in \MB{R}^K} \quad \|x'\|_1
\RM{s.t.} \quad Ax =y
\end{gather}
}

@@

\Result
{Definition}.
{
Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
For each integer \(S \in \MB{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\vartheta\) with \(\|\vartheta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
\begin{gather}
(1-\delta_S) \|\vartheta\|^2
\leq \|X_T \vartheta\|_2^2
\leq (1+\delta_S) \|\vartheta\|^2
\end{gather}
}

RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\vartheta_S\).

Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\vartheta_{S,S'}\) be the smallest constant such that
\begin{gather}
| \LA X_T c, X_{T'} c' \RA |
\leq \vartheta_{S,S'} \cdot \| c \|_2 \|c'\|_2
\end{gather}

@@

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
\begin{gather}
\min_{x' \in \MB{K}^p}  \|\hat{x'}\|_1 \\ \notag
\RM{subject}\; \RM{to} \quad \|A^\dagger r\|_\infty \leq \lambda_p \sigma
\end{gather}
where \(r =y -A \hat{x}\).
}
And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.

@@

With (), scholars often exploit the relation
\begin{gather}
\RM{vec}(Y)
=\big[ (F^\dagger) \otimes W \big] \RM{vec}(\M{H})
\end{gather}

@@

Since expression involving probability will get very complecated, introduce the direct product
%
\begin{gather}
\Omega
=\Omega_t \times \Omega_h \times \Omega_n \times \Omega_r
\end{gather}
%
to denote the overall sample space, where
%
\begin{itemize}
\item \(\Omega_t\) denotes the collection of probability samples at the transmitter end,
\item \(\Omega_h\) denotes that of the communication channel,
\item \(\Omega_h\) denotes that of the noise arising in the communication channel,
\item \(\Omega_r\) denotes that at the receiver end.
\end{itemize}
%
\(\omega_1\) stands for the event space index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.

We restrict our consideration to the uniform linear array, which can be modeled as
\begin{gather}
\V{a}(\varphi')
=\sum_{n=1}^{N} \RM{e}^{n \varphi' i} \V{u}_n
\end{gather}
where \(i\) is the imaginary unit, \(\V{u}_n\) is the unit vector of the \(n\)-th component.

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
\begin{gather}
H
=\sum_{l=0}^L \alpha_l \V{a}\big( \frac{d}{\lambda} \sin \varphi_l' \big) \V{a}\big( \frac{d_{\RM{arr}}}{\lambda} \sin \vartheta_l' \big)^\dagger
\end{gather}
The physical meaning of \(\vartheta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\vartheta_l\), the \(l\)-th that of arrival wave, while \(d_{\RM{arr}}\) is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \(\V{a}\) as
\begin{gather}
\varphi_l
=\frac{d_{\RM{arr}}}{\lambda} \sin \varphi_l' \\
\vartheta_l
=\frac{d_{\RM{arr}}}{\lambda} \sin \vartheta_l'
\end{gather}
to get a simpler form
\begin{gather}
H
=\sum_{l=0}^L \alpha_l \V{a}(\varphi_l) \V{a}(\vartheta_l)^\dagger
\end{gather}

@@

The effective channel \(\M{Y}\) has \(N_y\) columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \(\V{u}_n\).
This way, we may denote the acquired effective channel matrix \(\M{Y}\) under noisy observation as (borrowing Matlab's colon notation to denote columns)
\begin{gather}
\M{Y}(:,n)
:=\M{W}_B \M{W}_R ( \M{H} \M{F}_R \M{F}_B \V{u}_m +\V{z} ), \quad
n =1, 2, \dotsc, N_y
\end{gather}
The crux of the matter is the recovery of \(\M{H}\) with knowledge of \(\M{Y}\), and of course \(\M{W}_R, \M{W}_B, \M{F}_R, \M{F}_B\) which are in our control.

@@

Introduce the discrete Fourier matrix \(K\) defined to be
\begin{gather}
\M{K} \in \MB{M}(N_h, N_h) \\
\M{K}(n_1, n_2) =\frac{1}{\sqrt{N}} \RM{e}^{2\pi i n_1 n_2 /N},
\quad n_1, n_2 =0,1,2,\dotsc, N-1
\end{gather}
where \(i =\sqrt{-1}\).
And observe that, if we write
\begin{gather}
\M{G}
=\M{K}^\dagger \M{H}
\end{gather}
which has the interpretation as the spatial frequency domain representation of \(H\), then
\begin{gather}
\M{Y}
:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{F}_R \M{F}_B +\M{K}^\dagger \M{Z} )
\end{gather}
If at the end of day, \(G\) is sparse, then we recover \(G\) instead, and our use of DS is fully justified.
To the best of our knowledge, no work has explicitly considered the beamspace CSS.

That is to say, \(K^\dagger z\) may be absorbed, and a similar Kronecker product may be used.
\begin{gather}
\RM{vec}(Y)
\approx \big[ (F_B^\dagger F_R^\dagger) \otimes (W_B W_R K) \big] \RM{vec}(H)
\end{gather}
To simplify notation, set 
\begin{gather}
P =(F_B^\dagger F_R^\dagger) \otimes (W_B W_R K)
\end{gather}
The instances of \(P\) is completely determined in the transmitter and receiver end, that is
\begin{gather}
P =P(\omega_t, \omega_r)
\end{gather}
If so, our program reads

\Result
{Program}
{
Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
Suppose \(Y\) is the acquired effective channel matrix under corruption of noise \(z\).
\(P\) is defined just above in ().
Then, with parameter \(\gamma\) specified, define the following program
\begin{gather}
\hat{g}
=\underset {{h}} {\RM{min}} \|h\|_1 \quad
\RM{s.t.}\;\; \|P^\dagger (y -P h)\|_\infty \leq \gamma
\end{gather}
And convert \(\hat{g}\) back to the space domain as
\begin{gather}
\hat{h}
=K \hat{g}.
\end{gather}
And finally recover the estimated \(H\) as
\begin{gather}
\hat{H} =\RM{vec}^{-1} (\hat{h})
\end{gather}
}

@@

Consider
\begin{gather}
d =g -\hat{g}
\end{gather}
And let
\begin{itemize}
\item \(\MC{A}\) be the largest \(L\) position of \(g\).
\item \(\MC{B}\) be the largest \(L\) position of \(d\) except on \(\MC{A}\).
\item \(\MC{C} =\{1, \dotsc, N_h^2\} -( \MC{B} \cup \MC{C} )\), i.e., the complementary index set.
\end{itemize}
So \(\MC{A}, \MC{B}, \MC{C}\) are mutually exclusive index sets by construction:
\begin{gather}
\MC{A}, \MC{B}, \MC{C} \subset \{1, \dotsc, N_h^2\} \\
   \MC{A} \cap \MC{B} =\MC{B} \cap \MC{C} =\MC{A} \cap \MC{C} =\varnothing \\
\MC{A} \cup \MC{C} \cup \MC{C} =\{1, \dotsc, N\}.
\end{gather}

\Result
{Lemma.}
{
Let \(\varphi(\omega_h)\) and \(\vartheta(\omega_h)\) be both uniformly, independently distributed in \([0,2\pi)\), and beamspace channel matrix \(G\) defined as in ().
\begin{gather}
\|g_{\MC{A}}\|_1 \leq \frac{1}{\pi^2} \log \frac{L}{N}.
\end{gather}
}

@@

\Result
{Lemma}
{
\begin{align}
|\LA e, P_{:,j} \RA| \leq \sqrt{2 \log p}
\end{align}
}

\Result
{Lemma}
{
\begin{align}
\|P^\dagger P d\|_\infty
\leq& 2 \sqrt{2 \log p}.
\end{align}
}

To show this, start with
\begin{align}
\LA e -r, P_{:,j} \RA
=\LA P \hat{g} -P g, P_{:,j} \RA
=\LA P g, P_{:,j} \RA
\end{align}
Result follows from triangle inequality, and Lemma ().

From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result below.
The original result is for real vector spaces, but we have checked that the proof is completely valid in complex vector spaces.
Of course the interpretation of modulus and the inner product changes accordingly.

\Result
{Lemma}
{
\begin{align}
\|d_{\MC{A}}\|_2
\leq \frac{1}{1-\delta} \|P^\dagger_{\MC{A}\MC{B}} P \eta\|_2 +\frac{\vartheta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
\end{align}
}

From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result below.
Again, their proof works with complex vector spaces in place of real ones.

@@

\Result
{Definition}
{
For \(x \in \MB{R}^N\), We say \(\MC{R}(x) \in \MB{V}(2N)\) is the real representation of \(x\), defined by
\begin{gather}
x \in \MB{V}(2N^2) \notag \\
x(n) =
\begin{cases}
\MF{Re}(x(n)), &n =2n' \\
\MF{Im}(x(n)), &n =2n'+1
\end{cases} \\
n' =1, \dotsc, N \notag
\end{gather}
}

@@

\Result
{Definition}
{
For \(A \in \MB{M}(N_1,N_2)\), We say \(\MC{R}(A) \in \MB{M}(2N_1,2N_2)\) is the real representation of \(A\), defined by
\begin{gather}
A \in \MB{V}(2N^2) \notag \\
A(n_1,n_2) =
\begin{cases}
\MF{Re}(A(n_1,n_2)), &n_1 =2n_1'-1,\; n_2 =2n_2'-1  \\
\MF{Im}(A(n_1,n_2)), &n_1 =2n_1',\; n_2 =2n_2'-1  \\
-\MF{Im}(A(n_1,n_2)), &n_1 =2n_1'-1,\; n_2 =2n_2'  \\
\MF{Re}(A(n_1,n_2)), &n_1 =2n_1',\; n_2 =2n_2'  \\
\end{cases} \\
n_1' = 1, \dotsc, N_1 \notag \\
n_2' = 1, \dotsc, N_2 \notag
\end{gather}
}

@@

\Result
{Program}
{
Given are \(\T{P}, \T{y}, \gamma\).
Find \(\T{g}\) with
\begin{gather}
   \min_{\T{g}, \V{m}} \LA \V{1}, \V{m} \RA \notag \\
\RM{s.t.}
\begin{cases}
\| I_{n_h}^{(h)} \T{g} \|_2
   \leq \LA \V{y}_{n_h}, \V{m} \RA \\
\| I_{n_y}^{(y)} \T{P}^\dagger ( \T{P} \T{g} - \T{y} ) \|_2
\leq \gamma  \\
\end{cases}
\end{gather}
where \(\V{1}\) is the all-1 vector.
}

@@

\begin{align}
   &\MC{L}(\V{m}, \T{g}, \mu^{(h)}, \mu^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \notag \\
=& \LA \V{1}, m \RA 
   +\sum_{n_h} \big[ \LA \mu^{(h)}, I_{n_h}^{(h)} \T{g} \RA -\lambda^{(h)} \LA \V{y}_{n_h}, \V{m} \RA \big] \notag \\
\quad & +\sum_{n_y} \big[ \LA \mu^{(h)}, I_{n_y}^{(y)} \T{P}^\dagger ( \T{P} \T{g} -\T{u} ) \RA -\lambda^{(h)} \gamma \big]
\end{align}

>>>>

\author{Tzu-Yu Jeng}
\date{\today}

\title{Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound}

\newcommand{\MB}[1]{\mathbb{#1}}
\newcommand{\MC}[1]{\mathcal{#1}}
\newcommand{\MF}[1]{\mathfrak{#1}}
\newcommand{\RM}[1]{\mathrm{#1}}
\newcommand{\V}[1]{\stackunder[1.2pt]{$#1$}{\rule{.9ex}{.075ex}}}
\newcommand{\M}[1]{\V{\V{#1}}}
\newcommand{\T}[1]{\tilde{#1}}
\newcommand{\IP}[1]{\langle #1 \rangle}

\renewcommand{\H}{\dagger}

@@

We restrict our discussion to the Hilbert space over the field of \(\MB{R}\) or \(\MB{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
We use \(\MB{K}\) to refer to either \(\MB{R}\) or \(\MB{C}\).
Lower case Latin alphabets with single underline, like \(\V{a}\), denote vectors, and upper case Latin alphabets with double underlines, like \(\M{A}\), denote matrices.
To avoid being too pedantic, we simply write \(\V{a} \in \MB{C}^N\) to stress \(\V{a}\) is a \(N\)-dimensional vector, and the role it plays in the vector space is understood.
Similarly, we also write \(\V{A} \in \MB{M}(M,N)\) to stress \(\V{A}\) is a \(M\) by \(N\) matrix, and the role it plays as linear transformation is understood.
Inner product is denoted as \(\IP{ \MB{a}, \MB{b} }\).
Slightly abusing notation, denote as \(\V{a}(n)\) the \(n\)-th component of \(\V{a}\), and denote as \(\V{A}(m,n)\) the \((m,n)\)-entry of \(\V{A}\)
Especially, \(\V{u}_n\) is the \(n\)-th unit vector in the Cartesian coordinates (not to be confused with the noise).

@@

\Result
{Definition}
{
\(x \in \MB{K}^N\) is called \(s\)-sparse, if
\begin{gather} 
\# \RM{supp}(x) \leq s
\end{gather}
That is, only at most \(s\) components of vector \(x\) is nonzero.
}

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
\begin{gather}
\RM{min}_{x' \in \MB{R}^K}
\quad \|x'\|_1
\quad \RM{s.t.} \quad A x' =y
\end{gather}
}

@@

\Result
{Definition}.
{
Let \(A\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
For each integer \(S \in \MB{N}\), we say that \(A\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
\begin{gather}
(1-\delta_S) \|x\|^2
\leq \|A_T x\|_2^2
\leq (1+\delta_S) \|x\|^2
\end{gather}
}

RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\delta_S\).

Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\vartheta_{S,S'}\) be the smallest constant such that
\begin{gather}
| \IP{ X_T c, X_{T'} c' } |
\leq \vartheta_{S,S'} \cdot \| c \|_2 \|c'\|_2
\end{gather}

@@

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
\begin{gather}
\min_{x' \in \MB{K}^p}  \|\hat{x'}\|_1 \\ \notag
\RM{subject}\; \RM{to} \quad \|A^\H r\|_\infty \leq \lambda_p \sigma
\end{gather}
where \(r =y -A \hat{x}\).
}
And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.

@@

With (), scholars often exploit the relation
\begin{gather}
\RM{vec}(Y)
=\big[ (F^\H) \otimes W \big] \RM{vec}(\M{H})
\end{gather}

@@

Since expression involving probability will get very complecated, introduce the direct product
\begin{gather}
\Omega
=\Omega_t \times \Omega_h \times \Omega_n \times \Omega_r
\end{gather}
to denote the overall sample space, where

\begin{itemize}
\item \(\Omega_t\) denotes the collection of probability samples at the transmitter end,
\item \(\Omega_h\) denotes that of the communication channel,
\item \(\Omega_h\) denotes that of the noise arising in the communication channel,
\item \(\Omega_r\) denotes that at the receiver end.
\end{itemize}
%
\(\omega_1\) stands for the event space index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.

We restrict our consideration to the uniform linear array, which can be modeled as
\begin{gather}
\V{a} \in \MB{V}(N_h) \\
\V{a}(\psi')
=\sum_{n=1}^{N} \RM{e}^{n \psi' i} \V{u}_n
\end{gather}
where \(i\) is the imaginary unit, \(\V{u}_n\) is the unit vector of the \(n\)-th component.

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
\begin{gather}
H
=\sum_{l=0}^L \alpha_l \V{a}\big( \frac{d}{\lambda} \sin \varphi_l' \big) \V{a}\big( \frac{d_{\RM{arr}}}{\lambda} \sin \vartheta_l' \big)^\H
\end{gather}
The physical meaning of \(\vartheta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\vartheta_l\), the \(l\)-th that of arrival wave, while \(d_{\RM{arr}}\) is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \(\V{a}\) as
\begin{gather}
\varphi_l
=\frac{d_{\RM{arr}}}{\lambda} \sin \varphi_l' \\
\vartheta_l
=\frac{d_{\RM{arr}}}{\lambda} \sin \vartheta_l'
\end{gather}
to get a simpler form
\begin{gather}
H
=\sum_{l=0}^L \alpha_l \V{a}(\varphi_l) \V{a}(\vartheta_l)^\H
\end{gather}

@@

The effective channel \(\M{Y}\) has \(N_y\) columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \(\V{u}_n\).
This way, we may denote the acquired effective channel matrix \(\M{Y}\) under noisy observation as (borrowing Matlab's colon notation to denote columns)
\begin{gather}
\M{Y}(:,n)
:=\M{W}_B \M{W}_R ( \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} ), \quad
n_y =1, 2, \dotsc, N_y
\end{gather}
The crux of the matter is the recovery of \(\M{H}\) with knowledge of \(\M{Y}\), and of course \(\M{W}_R, \M{W}_B, \M{F}_R, \M{F}_B\) which are in our control.

@@

Introduce the discrete Fourier matrix \(\M{K}\) defined to be
\begin{gather}
\M{K} \in \MB{M}(N_h, N_h) \\
\M{K}(n_1, n_2) =\frac{1}{\sqrt{N}} \RM{e}^{2\pi i n_1 n_2 /N},
\quad n_1, n_2 =0,1,2,\dotsc, N-1
\end{gather}
where \(i =\sqrt{-1}\).
And observe that, if we write
\begin{gather}
\M{G}
=\M{K}^\H \M{H}
\end{gather}
which has the interpretation as the spatial frequency domain representation of \(\M{H}\), then
\begin{gather}
\M{Y}
:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
\end{gather}
If at the end of day, \(\M{G}\) is sparse, then we recover \(\M{G}\) instead, and our use of DS is fully justified.
To the best of our knowledge, no work has explicitly considered the beamspace CSS.

That is to say, \(\M{K}^\H \V{z}\) may be absorbed, and a similar Kronecker product may be used.
\begin{gather}
\RM{vec}(\M{Y})
\approx \big[ (\M{F}_B^\H \M{F}_R^\H) \otimes (\M{W}_B \M{W}_R \M{K}) \big] \RM{vec}(\M{H})
\end{gather}
To simplify notation, set 
\begin{gather}
\M{P} =(\M{F}_B^\H \M{F}_R^\H) \otimes (\M{W}_B \M{W}_R \M{K})
\end{gather}
The instances of \(\M{P}\) is completely determined in the transmitter and receiver end, that is
\begin{gather}
\M{P} =\M{P}(\omega_t, \omega_r)
\end{gather}
If so, our program reads

\Result
{Program}
{
Let \(\M{H}(\omega_h, \omega_n)\) be the virtual channel, and \(\M{W}_R(\omega_r)\) the random analog combiner, \(\M{W}_B(\omega_r)\) the random analog combiner, \(\M{F}_R(\omega_t)\) the random analog combiner, \(\M{F}_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
Suppose \(\M{Y}\) is the acquired effective channel matrix under corruption of noise \(\V{z}\).
\(\M{P}\) is defined just above in ().
Then, with parameter \(\gamma\) specified, define the following program
\begin{gather}
\hat{\V{g}}
=\underset {\V{h}} {\RM{min}} \|\V{h}\|_1 \quad
\RM{s.t.}\quad \|P^\H (y -P h)\|_\infty \leq \gamma
\end{gather}
And convert \(\hat{g}\) back to the space domain as
\begin{gather}
\hat{h}
=K \hat{g}.
\end{gather}
And finally recover the estimated \(H\) as
\begin{gather}
\hat{H} =\RM{vec}^{-1} (\hat{h})
\end{gather}
}

@@

Consider
\begin{gather}
d =g -\hat{g}
\end{gather}
And let
\begin{itemize}
\item \(\MC{A}\) be the largest \(L\) position of \(g\).
\item \(\MC{B}\) be the largest \(L\) position of \(d\) except on \(\MC{A}\).
\item \(\MC{C} =\{1, \dotsc, N_h^2\} -( \MC{B} \cup \MC{C} )\), i.e., the complementary index set.
\end{itemize}
So \(\MC{A}, \MC{B}, \MC{C}\) are mutually exclusive index sets by construction:
\begin{gather}
\MC{A}, \MC{B}, \MC{C} \subset \{1, \dotsc, N_h^2\} \\
\MC{A} \cap \MC{B} =\MC{B} \cap \MC{C} =\MC{A} \cap \MC{C} =\varnothing \\
\MC{A} \cup \MC{B} \cup \MC{C} =\{1, \dotsc, N\}.
\end{gather}

\Result
{Lemma}
{
Let \(\varphi(\omega_h)\) and \(\vartheta(\omega_h)\) be both uniformly, independently distributed in \([0,2\pi)\), and beamspace channel matrix \(G\) defined as in ().
\begin{gather}
\|g_{\MC{A}}\|_1 \leq \frac{1}{\pi^2} \log \frac{L}{N}.
\end{gather}
}

@@

\Result
{Lemma}
{
\begin{align}
|\IP{ e, P_{:,j} }| \leq \sqrt{2 \log p}
\end{align}
}

\Result
{Lemma}
{
\begin{align}
\|P^\H P d\|_\infty
\leq& 2 \sqrt{2 \log p}.
\end{align}
}

To show this, start with
\begin{align}
\IP{ z -(y -P h), P(:,n_y) }
=\IP{ P \hat{g} -P g, P(:,n_y) }
=\IP{ P g, P(:,n_y) }
\end{align}
Result follows from triangle inequality, and Lemma ().

From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result as below.
The original result is for real vector spaces, but we have checked that the proof is completely valid in complex vector spaces.
Of course the interpretation of modulus and the inner product changes accordingly.

\Result
{Lemma}
{
\begin{align}
\|d_{\MC{A}}\|_2
\leq \frac{1}{1-\delta} \|P^\H_{\MC{A}\MC{B}} P \eta\|_2 +\frac{\vartheta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
\end{align}
}

From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result as below.
Again, their proof works with complex vector spaces in place of real ones too.

@@

\Result
{Definition}
{
For \(x \in \MB{V}(M)\), We say \(\MC{R}(x) \in \MB{V}(2M)\) is the real representation of \(x\), defined by
\begin{gather}
x \in \MB{V}(2M^2) \notag \\
x(m) =
\begin{cases}
\MF{Re}(x(m)), &m =2m' \\
\MF{Im}(x(m)), &m =2m'+1
\end{cases} \\
m' =1, \dotsc, M \notag
\end{gather}
}

@@

\Result
{Definition}
{
For \(A \in \MB{M}(m_1,m_2)\), We say \(\MC{R}(A) \in \MB{M}(2m_1,2m_2)\) is the real representation of \(A\), defined by
\begin{gather}
A \in \MB{V}(2M^2) \notag \\
A(m_1,m_2) =
\begin{cases}
\MF{Re}(A(m_1,m_2)), &m_1 =2m_1'-1,\; m_2 =2m_2'-1  \\
\MF{Im}(A(m_1,m_2)), &m_1 =2m_1',\; m_2 =2m_2'-1  \\
-\MF{Im}(A(m_1,m_2)), &m_1 =2m_1'-1,\; m_2 =2m_2'  \\
\MF{Re}(A(m_1,m_2)), &m_1 =2m_1',\; m_2 =2m_2'  \\
\end{cases} \\
m_1' = 1, \dotsc, m_1 \notag \\
m_2' = 1, \dotsc, m_2 \notag
\end{gather}
}

@@

\Result
{Program}
{
Given are \(\T{P}, \T{y}, \gamma\).
Find \(\T{g}\) with
\begin{gather}
   \min_{\T{g}, \V{m}} \IP{ \V{1}, \V{m} } \notag \\
\RM{s.t.}
\begin{cases}
\| I_{n_h}^{(h)} \T{g} \|_2
   \leq \IP{ \V{y}_{n_h}, \V{m} } \\
\| I_{n_y}^{(y)} \T{P}^\H ( \T{P} \T{g} - \T{y} ) \|_2
\leq \gamma  \\
\end{cases}
\end{gather}
where \(\V{1}\) is the all-1 vector.
}

@@

\begin{align}
   &\MC{L}(\V{m}, \T{g}, \mu^{(h)}, \mu^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \notag \\
=& \IP{ \V{1}, m } 
   +\sum_{n_h} \big[ \IP{ \mu^{(h)}, I_{n_h}^{(h)} \T{g} } -\lambda^{(h)} \IP{ \V{y}_{n_h}, \V{m} } \big] \notag \\
\quad & +\sum_{n_y} \big[ \IP{ \mu^{(h)}, I_{n_y}^{(y)} \T{P}^\H ( \T{P} \T{g} -\T{u} ) } -\lambda^{(h)} \gamma \big]
\end{align}
